%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Konstantinos Xirogiannopoulos} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{3226 A.V. Williams Bldg} % Your address
\moveleft.5\hoffset\centerline{College Park, MD 20740}
\moveleft.5\hoffset\centerline{(xxx) xxxx-xxx}
\moveleft.5\hoffset\centerline{\href{mailto:kostasx@cs.umd.edu}{kostasx@cs.umd.edu}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{INTERESTS}

I am interested in database systems, big data management, large-scale analytics and distributed systems

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl PhD. in Computer Science,}  \hfill August 2014 - current \\
University of Maryland, College Park\\

{\sl BSc. in Computer Science,}  \hfill September 2009 - January 2014 \\
Bachelor of Science in Computer Science,\\
\textit{Ranked in the top 7.5\% of graduates in past five years)}
Athens University of Economics and Business\\
% {\sl PhD. in Computer Science,}  \hfill August 2014 - August 2015 \\
% Athens University of Economics and Business, Athens, Greece\\

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS}

{\sl Programming Languages:} Python, Java, C\#, JavaScript, C, C++. \\
{\sl Web Backend Technologies:} Django, Django REST Framework, Mongo, MongoEngine, PostgreSQL, MySQL, Mandrill, AmazonS3, Heroku. \\
{\sl Web Frontend Technologies:} AngularJS, JQuery, JQueryMobile, Bootstrap, Firebase. \\
{\sl Software Engineering:} Agile, Scrum, Version control, Requirements analysis. \\
{\sl Software:} Atlassian Suite, Vagrant, Git, Vim, VirtualEnv, VirtualBox, Ansible, Gulp. \\

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Owner} \hfill November 2013 - Present \\
E \& F Technologies, Kennesaw, GA
\begin{itemize}
\item Created a business that develops software to assess and maintain risk at large events for Greek organizations.
\item Developed software written in Python, JavaScript, HTML5, and CSS.
\end{itemize}

{\sl Software Engineer} \hfill August 2013 - Present \\
Georgia Tech Research Institute, Electronic Systems Laboratory, Atlanta, GA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and Developed Django/AngularJS software systems for the Department of Defense, Army, and Navy.
\item Presented software demos to Department of Defense derived clients.
\end{itemize}

{\sl Independent Software Contractor} \hfill May 2014 - September 2014\\
JTE Technologies, Kennesaw, GA
\begin{itemize}
\item Performed the full software development process with the end result of deploying a large scale software system that manages access to high priority physical and logical assets.
\item Designed the architecture for a Django/AngularJS software system.
\end{itemize}


%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{COMMUNITY \\ SERVICE}

Kennesaw Mountain Trail Club, {\sl Volunteer} \hfill February 2014 - Present \\
Race Against Violence, {\sl Volunteer} \hfill October 2012 - Present \\

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES}

Kappa Sigma Fraternity, {\sl President} \hfill August 2014 - Present\\
Kappa Sigma Fraternity, {\sl Treasurer} \hfill December 2013 - August 2014 \\
Technology Student Association, {\sl Team Leader} \hfill August 2011 - May 2012 \\


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
